Potential Factors of Decreasing Birth Rates in the US since the Great Recession and Beyond

### 2024-02-10 outputs/paper/paper.qmd
Update

---
title: "Potential Factors of Decreasing Birth Rates in the US since the Great Recession and Beyond"
subtitle: "Reproduction of 'The Puzzle of Falling US Birth Rates since the Great Recession'(Kearney, Levine & Pardue, 2022)"
author: 
  - Chay Park
thanks: "Code and data are available at: https://github.com/Chay-HyunminPark/Social-Science-Study."
date: today
date-format: long
abstract: "Decreasing birth rates became the conversation topic globally in recent years. Kearney, Levine, and Pardue (2022) analyzed possible factors in demographical, economical and social aspects from the period 1980 to 2020. By reproducing some applications of the 'The Puzzle of Falling US Birth Rates Since the Great Recession,' this paper demonstrate potential factors correlating aspects on economics, religions, laws and enforcement applied in each states."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

We replicate the paper by Kearney, Levine, and Pardue (2022) with a focus on the following research questions: 
- What is the trend in the US birth rates over the period 1980 to 2020?
- How does the birth rates vary by the age group?
- How does the birth rates vary by the race and ethnicity of mothers'?

@@

# Plotting the data
ggplot(data, aes(x = year, y = brate_all)) +
  geom_line(color = "blue") +
  geom_vline(xintercept = 2007, linetype = "dotted") +
  annotate("text", x = 2007, y = 80, label = "2007", vjust = -0.5, hjust = 0.5, color = "black") +
  geom_hline(yintercept = seq(50, 80, by = 5), color = "lightgrey") +
  scale_y_continuous(limits = c(50, 80), breaks = seq(50, 80, by = 5)) +
  scale_x_continuous(limits = c(1980, 2020), breaks = seq(1980, 2020, by = 1), labels = function(x) ifelse(x %% 5 == 0, x, "")) +
  labs(x = "Year", y = "Births per 1,000 women age 15-44",
       title = "Trend in US Birth Rates",
       caption = "Birth Rates collected from CDC Vital Statistics Births Reports for 2015, 2019, and 2020.") +
  theme_classic()
```
Figure 1 Trend in US Birth Rates, not just the Great Recession was there another events? 
낙태법 시행일, 법적으로 진행된 일, economic crisis other than great recession

@@

# Plotting the first line graph (Graph A)
graph_A <- ggplot(data, aes(x = year)) +
  geom_line(aes(y = brate_1519, color = "blue"), size = 0.4) +
  geom_line(aes(y = brate_2024, color = "orange"), size = 0.4) +
  geom_line(aes(y = brate_2529, color = "grey"), size = 0.4) +
  geom_line(aes(y = brate_3034, color = "yellow"), size = 0.4) +
  geom_line(aes(y = brate_3539, color = "cyan"), size = 0.4) +
  geom_line(aes(y = brate_4044, color = "green"), size = 0.4) +
  geom_text(data = data[data$year == 2020,], aes(x = year, y = brate_1519, label = "Age 15-19"), hjust = -0.1, vjust = -0.5, size = 2, family = "Times") +
  geom_text(data = data[data$year == 2020,], aes(x = year, y = brate_2024, label = "Age 20-24"), hjust = -0.1, vjust = -0.5, size = 2, family = "Times") +
  geom_text(data = data[data$year == 2020,], aes(x = year, y = brate_2529, label = "Age 25-29"), hjust = -0.1, vjust = -0.5, size = 2, family = "Times") +
  geom_text(data = data[data$year == 2020,], aes(x = year, y = brate_3034, label = "Age 30-34"), hjust = -0.1, vjust = -0.5, size = 2, family = "Times") +
  geom_text(data = data[data$year == 2020,], aes(x = year, y = brate_3539, label = "Age 35-39"), hjust = -0.1, vjust = -0.5, size = 2, family = "Times") +
  geom_text(data = data[data$year == 2020,], aes(x = year, y = brate_4044, label = "Age 40-44"), hjust = -0.1, vjust = -0.5, size = 2, family = "Times") +
  geom_vline(xintercept = 2007, linetype = "dotted") +
  annotate("text", x = 2007, y = 120, label = "2007", vjust = -0.5, hjust = 0.5, color = "black", family = "Times") +
  geom_hline(yintercept = seq(0, 140, by = 20), color = "lightgrey") +
  scale_y_continuous(limits = c(0, 140), breaks = seq(0, 140, by = 20), labels = seq(0, 140, by = 20)) +
  scale_x_continuous(limits = c(1980, 2020), breaks = seq(1980, 2020, by = 1), labels = function(x) ifelse(x %% 5 == 0, x, "")) +
  labs(x = NULL, 
       y = 'Births per 1,000 women in relevant population subgroup',
       title = "A: Five-year age group",
       caption = NULL,
       family = "Times") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = -45, hjust = 1, family = "Times", size = 5),
        plot.title = element_text(size = 7, family = "Times"),
        legend.position = "none")

# Plotting the second line graph (Graph B)
graph_B <- ggplot(data, aes(x = year)) +
  geom_line(aes(y = brate_hisp, color = "grey"), size = 0.4) +
  geom_line(aes(y = brate_blacknh, color = "orange"), size = 0.4) +
  geom_line(aes(y = brate_whitenh, color = "blue"), size = 0.4) +
  geom_text(data = data[data$year == 2020,], aes(x = year, y = brate_hisp, label = "Hispanic"), size = 2, family = "Times") +
  geom_text(data = data[data$year == 2020,], aes(x = year, y = brate_blacknh, label = "Black, non-Hispanic"), size = 2, family = "Times") +
  geom_text(data = data[data$year == 2020,], aes(x = year, y = brate_whitenh, label = "White, non-Hispanic"), size = 2, family = "Times") +
  geom_vline(xintercept = 2007, linetype = "dotted") + annotate("text", x = 2007, y = 120, label = "2007", color = "black", family = "Times") +
  geom_hline(yintercept = seq(0, 140, by = 20), color = "lightgrey") + scale_y_continuous(limits = c(0, 140), breaks = seq(0, 140, by = 20), labels = seq(0, 140, by = 20)) + scale_x_continuous(limits = c(1990, 2020), breaks = seq(1990, 2020, by = 1), labels = function(x) ifelse(x %% 5 == 0, x, "")) + labs(x = NULL, y = NULL,
       title = "B: Race and ethnicity (ages 15-44)",
       caption = "Birth rates by age group, race, and ethnicity, and marital status gathered from CDC Vital Statistics Births Reports. Birth rates by Hispanic subpopulation, mother's education are calculated by the original author's using NCHS Vital Statistics birth micro data, SEER population data, and the Current Population Survey.") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = -45, hjust = 1, family = "Times", size = 5),
        plot.title = element_text(size = 7, family = "Times"),
        legend.position = "none")

@@

```{r}
# Load necessary libraries
library(dplyr)
library(knitr)
library(kableExtra)

@@

Figure 3 B, major religion of Hispanic, Black, White  religious reason of each race and ethnicity

>>>>

---
title: "Potential Factors of Decreasing Birth Rates in the US since the Great Recession and Beyond"
subtitle: "Reproduction of 'The Puzzle of Falling US Birth Rates since the Great Recession'(Kearney, Levine & Pardue, 2022)"
author: 
  - Chay Park
thanks: "Code and data are available at: https://github.com/Chay-HyunminPark/Social-Science-Study."
date: today
date-format: long
abstract: "Decreasing birth rates became the conversation topic globally in recent years. Kearney, Levine, and Pardue (2022) analyzed possible factors in demographical, economical and social aspects from the period 1980 to 2020. By reproducing some applications of the 'The Puzzle of Falling US Birth Rates Since the Great Recession,' this paper demonstrate potential factors correlating aspects on economics, religions, laws and enforcement applied in each states."
format: pdf
number-sections: true
bibliography: references.bib
prefer-html: true
---

@@

We replicate the paper by Kearney, Levine, and Pardue (2022) with a focus on the following research questions:

* What is the trend in the US birth rates over the period 1980 to 2020?

* How does the birth rates vary by the age group?

* How does the birth rates vary by the race and ethnicity of mothers'?

@@

# Plotting the data
ggplot(data, aes(x = year, y = brate_all)) +
  geom_line(color = "blue") +
  geom_vline(xintercept = 2007, linetype = "dotted") +
  annotate("text", x = 2007, y = 80, label = "2007", vjust = -0.5, hjust = 0.5, color = "black") +
  geom_hline(yintercept = seq(50, 80, by = 5), color = "lightgrey") +
  scale_y_continuous(limits = c(50, 80), breaks = seq(50, 80, by = 5)) +
  scale_x_continuous(limits = c(1980, 2020), breaks = seq(1980, 2020, by = 1), labels = function(x) ifelse(x %% 5 == 0, x, "")) +
  labs(x = "Year", y = "Births per 1,000 women age 15-44",
       caption = "Birth Rates collected from CDC Vital Statistics Births Reports for 2015, 2019, and 2020.") +
  theme_classic()
```

Figure 1 Trend in US Birth Rates, not just the Great Recession was there another events? 
낙태법 시행일, 법적으로 진행된 일, economic crisis other than great recession

@@

# Plotting the first line graph (Graph A)
graph_A <- ggplot(data, aes(x = year)) +
  geom_line(aes(y = brate_1519, color = "blue"), size = 0.4) +
  geom_line(aes(y = brate_2024, color = "orange"), size = 0.4) +
  geom_line(aes(y = brate_2529, color = "grey"), size = 0.4) +
  geom_line(aes(y = brate_3034, color = "yellow"), size = 0.4) +
  geom_line(aes(y = brate_3539, color = "cyan"), size = 0.4) +
  geom_line(aes(y = brate_4044, color = "green"), size = 0.4) +
  geom_text(data = data[data$year == 2020,], aes(x = year, y = brate_1519, label = "Age 15-19"), hjust = -0.1, vjust = -0.5, size = 2, family = "Times") +
  geom_text(data = data[data$year == 2020,], aes(x = year, y = brate_2024, label = "Age 20-24"), hjust = -0.1, vjust = -0.5, size = 2, family = "Times") +
  geom_text(data = data[data$year == 2020,], aes(x = year, y = brate_2529, label = "Age 25-29"), hjust = -0.1, vjust = -0.5, size = 2, family = "Times") +
  geom_text(data = data[data$year == 2020,], aes(x = year, y = brate_3034, label = "Age 30-34"), hjust = -0.1, vjust = -0.5, size = 2, family = "Times") +
  geom_text(data = data[data$year == 2020,], aes(x = year, y = brate_3539, label = "Age 35-39"), hjust = -0.1, vjust = -0.5, size = 2, family = "Times") +
  geom_text(data = data[data$year == 2020,], aes(x = year, y = brate_4044, label = "Age 40-44"), hjust = -0.1, vjust = -0.5, size = 2, family = "Times") +
  geom_vline(xintercept = 2007, linetype = "dotted") +
  annotate("text", x = 2007, y = 120, label = "2007", vjust = -0.5, hjust = 0.5, color = "black", family = "Times") +
  geom_hline(yintercept = seq(0, 140, by = 20), color = "lightgrey") +
  scale_y_continuous(limits = c(0, 140), breaks = seq(0, 140, by = 20), labels = seq(0, 140, by = 20)) +
  scale_x_continuous(limits = c(1980, 2020), breaks = seq(1980, 2020, by = 1), labels = function(x) ifelse(x %% 5 == 0, x, "")) +
  labs(x = NULL, 
       y = 'Births per 1,000 women in relevant population subgroup',
       title = "A: Five-year age group",
       caption = NULL,
       family = "Times") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = -45, hjust = 1, family = "Times", size = 8),
        plot.title = element_text(size = 10, family = "Times"),
        legend.position = "none")

# Plotting the second line graph (Graph B)
graph_B <- ggplot(data, aes(x = year)) +
  geom_line(aes(y = brate_hisp, color = "grey"), size = 0.4) +
  geom_line(aes(y = brate_blacknh, color = "orange"), size = 0.4) +
  geom_line(aes(y = brate_whitenh, color = "blue"), size = 0.4) +
  geom_text(data = data[data$year == 2020,], aes(x = year, y = brate_hisp, label = "Hispanic"), size = 2, family = "Times") +
  geom_text(data = data[data$year == 2020,], aes(x = year, y = brate_blacknh, label = "Black, non-Hispanic"), size = 2, family = "Times") +
  geom_text(data = data[data$year == 2020,], aes(x = year, y = brate_whitenh, label = "White, non-Hispanic"), size = 2, family = "Times") +
  geom_vline(xintercept = 2007, linetype = "dotted") + annotate("text", x = 2007, y = 120, label = "2007", color = "black", family = "Times") +
  geom_hline(yintercept = seq(0, 140, by = 20), color = "lightgrey") + scale_y_continuous(limits = c(0, 140), breaks = seq(0, 140, by = 20), labels = seq(0, 140, by = 20)) + scale_x_continuous(limits = c(1990, 2020), breaks = seq(1990, 2020, by = 1), labels = function(x) ifelse(x %% 5 == 0, x, "")) + labs(x = NULL, y = NULL,
       title = "B: Race and ethnicity (ages 15-44)",
       caption = "Birth rates by age group, race, and ethnicity, and marital status gathered from CDC Vital Statistics Births Reports. Birth rates by Hispanic subpopulation, mother's education are calculated by the original author's using NCHS Vital Statistics birth micro data, SEER population data, and the Current Population Survey.") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = -45, hjust = 1, family = "Times", size = 8),
        plot.title = element_text(size = 10, family = "Times"),
        legend.position = "none")

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: tbl-trendssub-table
#| tbl-cap: "Trends in Birth Rates by Population Race and Ethnicity"

# Load necessary libraries
library(dplyr)
library(knitr)
library(kableExtra)

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-trendssub-graph
#| fig-cap: "Trends in Birth Rates by Population Race and Ethnicity"

# Load required libraries
library(dplyr)
library(ggplot2)

# Refer to the table a
# Assume selected_data contains the relevant data

# Create bar graphs for each racial/ethnic group
bar_plot <- ggplot(selected_data, aes(x = Year)) +
  geom_bar(aes(y = Hispanic, fill = "Hispanic"), stat = "identity", position = "stack") +
  geom_bar(aes(y = Black, fill = "Black"), stat = "identity", position = "stack") +
  geom_bar(aes(y = White, fill = "White"), stat = "identity", position = "stack") +
  labs(x = "Year",
       y = "Births per 1,000 women relevant population subgroup") +
  scale_fill_manual(values = c(Hispanic = "grey", Black = "orange", White = "blue"),
                    name = "Race and ethnicity") +
  theme_minimal() +
  scale_x_continuous(breaks = seq(1990, 2020, by = 5), minor_breaks = seq(1990, 2020, by = 1)) +
  ylim(0, 120)

# Print the bar plot
print(bar_plot)
```
Figure 3 B, major religion of Hispanic, Black, White  religious reason of each race and ethnicity
